models with mice

### 2024-03-17 withmice.Rmd
finished nuclear risk perception computations. removed reverse coding from FA options and chapter 2

---
title: "models with mice"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    keep_tex: yes
  keep_md: yes
---

@@

@@

demobar$State <- factor(demobar$State, levels = c("Maharashtra","Rajasthan", "West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
demobar$age <- factor(demobar$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
demobar$urban_rural <- factor(demobar$urban_rural, levels = c("Rural","Urban"))
demobar$gender <- factor(demobar$gender, levels = c("Male","Female"))
demobar$caste <- factor(demobar$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
demobar$religion <- factor(demobar$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

@@

n_acceptreject<- codedmodule2 %>%
                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

@@

@@

@@

\blandscape

@@

fa_table(fit , .4) %>%
  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
  flex("EFA: Kahan Scale", col_widths = list(Items = 4.5, Code = 1))

@@

\elandscape

```{r, echo = FALSE}
fit[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Hierarchy_Egalitarianism = MR1, Communitarianism = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Kahan Scale")
```

@@

nkahanall <- kahanallscores %>%
  rowwise() %>%
  mutate( K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH"))),
    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

@@

@@

# PRIDENUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "PRIDENUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the PRIDENUCLEAR variable.") 
```

@@

miecopol <- mifa(data= ecopoln,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

@@

ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 5, seed = 429, print = FALSE), "broad")

@@

@@

radar4 <- rbind(max_min2, wide_loadings_df2) %>%
    rename(
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Limits on Wealth " = "WEALTHLIM",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Pro Centralisation" = "DECISIONCEN",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Anti Regulations" = "OWNERNOREG",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Reliance on government(nuclear)" = "RELYNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Environment over Development" = "ENVOVERDEV",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Localeconomy" = "ECONOMYLOCAL",
    )

@@

```{r, echo=FALSE, fig.width=15, fig.height=7, out.width='70', out.height='70'}
library(fmsb)

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.7), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "black", cglty = 1, cglwd = 2,
    # Customize the axis
    axislabcol = "black", cexc = 1.5, # Increase label size for axis
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
    seg = 7, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 4,
    ...
  )
}

@@

# Pretty table attempt 1

\blandscape
# FA on Combined Scale (2 Factor Solution): People Centered Development and Nationalist Development 
## Nuclear Energy: EFA on Combined Scale (2 Factor Solution)

@@

rename_map2 <- c(
  "Limits on Wealth" = "A limit should be put to how much wealth a person can amass",
  "Anti Mechanisation of work" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "Pro Decentralisation" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "Pro Centralisation" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "Pro Large Industries" = "Large scale industries are required for the development of the country that will benefit everyone",
  "Anti Large Industries" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "Pro Globaleconomy" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "Pro Localeconomy" = "India would be better off if foreign companies didn't come to here",
  "Environment over Development" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "Development over Environment" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "Pro Private ownership" = "All businesses and industries should be owned privately",
  "Anti Regulations" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "Pro Public ownership" = "The government should own most large businesses and industries",
  "Pro Regulations" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "Displacement risk(nuclear)" = "Nuclear energy is leading to displacement of people from their land",
  "Spoils Natural Beauty(nuclear)" = "Nuclear energy spoils the natural beauty of the landscape",
  "Pollution risk(nuclear)" = "Nuclear energy increases pollution of air/water/land",
  "Health risk(nuclear)" = "Nuclear energy poses a great risk to the health of people living around it",
  "Job opportunities(nuclear)" = "Nuclear energy will bring jobs to the local community",
  "Community pride(nuclear)" = "I would be proud if my community used nuclear energy",
  "National pride(nuclear)" = "Nuclear energy is a mark of pride for our nation",
  "National development(nuclear)" = "Nuclear energy pushes forward the country's development",
  "Local prosperity(nuclear)" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "Reliance on government(nuclear)" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

@@

fa_table(ecopolfit2, .4) %>%
  rename(Ndevelop = MR1, Pdevelop = MR2, Items= item) %>%
  flex("2 factor solution", col_widths = list(Items = 4.5, code = 1.5))

@@

\elandscape

```{r, echo = FALSE}
ecopolfit2[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Ndevelop = MR1, Pdevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Combined Scale (2 Factor Solution)")
```

@@

kahannuclear <- fct_scores%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

@@

# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
#pred[, "Uppercaste"] <- 0
#pred[, "Male"] <- 0
#pred[, "Hindu"] <- 0
#pred[, "Age"] <- 0
#pred[, "Ndevelop"] <- 0
#pred[, "Pdevelop"] <- 0
#pred[, "Hierarchy_Egalitarian"] <- 0
#pred[, "Communitarian"] <- 0
# Identify columns that start with "K_" and set them to 0
#k_columns <- grep("^K_", colnames(formice1))
#pred[, k_columns] <- 0

@@

nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice)

nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice)

@@

kahannuclear2 <- fct_scoresk2%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice2)

nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice2)

@@

kahannuclear3 <- fct_scoresk3%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice3)

nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice3)

@@

kahannuclear4 <- fct_scoresk4%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice4)

nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice4)

@@

kahannuclearfinal <- nkahanfinal%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

@@

@@

nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformicefinal)

nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)

#summary(nuclearfinal)
#summary(nuclearfinal2)
#summary(nuclearfinal3)
#summary(nuclearfinal4)
```

\newpage
\blandscape

@@

\elandscape

>>>>

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

# Bar plot: STATE X PDEVELOP

```{r}

# Load necessary libraries
library(dplyr)
library(ggplot2)
library(forcats)

# Df to include relevant variables

WBques <- module2 %>%  filter(!row_number() %in% c(1,2)) %>% dplyr::select(State, DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR ) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

levels_defined <- c("Strongly agree", "Somewhat agree","Neither agree nor disagree", "Somewhat disagree","Strongly disagree","Rather not say/Don't know")

WBques_factors <- WBques
WBques_factors[] <- lapply(names(WBques_factors), function(colname) {
  if (colname != "State") {
    factor(WBques_factors[[colname]], levels = levels_defined)
  } else {
    WBques_factors[[colname]] # Keep the State column unchanged
  }
})

WBques_factors$State <- factor(WBques_factors$State, 
                               levels = c("West Bengal", "Uttar Pradesh", "Maharashtra", "Rajasthan", "Tamil Nadu"))

library(dplyr)
library(ggplot2)

# Assuming your updated data frame is named WBques_factors

# Create a summary table with counts for each level of DISPLACENUCLEAR within each State
WBques_summary <- WBques_factors %>%
  count(State, DISPLACENUCLEAR) %>%
  group_by(State) %>%
  mutate(Proportion = n / sum(n))

# Create a named vector with full statements for each variable
full_statements <- c(DISPLACENUCLEAR = "Nuclear energy is leading to displacement of people from their land",
                     BEAUTYNUCLEAR = "Nuclear energy spoils the natural beauty of the landscape",
                     POLLUTENUCLEAR = "Nuclear energy increases pollution of air/water/land",
                     HEALTHNUCLEAR = "Nuclear energy poses a great risk to the health of people living around it",
                     ENVOVERDEV = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs")

# Reshape the data to long format for the selected variables
WBques_long <- WBques_factors %>%
  pivot_longer(cols = c(DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR),
               names_to = "Question",
               values_to = "Response") %>%
  mutate(Question = recode(Question, !!!full_statements)) # Replace var names with full statements

# Create a summary table with proportions for each level of Response within each State and Question
WBques_summary <- WBques_long %>%
  count(State, Question, Response) %>%
  group_by(State, Question) %>%
  mutate(Proportion = n / sum(n))

# Define the color sequence, with the darkest red for "Strongly agree"
colorsequence <- c("#8C4646","#D9695F","#F2A679","#F2D091","#FFF2CC","#808080")

# Plot the graph with facets for each Question
ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_manual(values = rev(colorsequence), name = NULL) +
  facet_wrap(~ Question, scales = "free_y", ncol = 1) +
  coord_flip() +
  labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
  theme_minimal() +
  theme(
    # Increase the size of the main title
    plot.title = element_text(size = 16, face = "bold"),
    # Increase the size of the axis titles
    axis.title = element_text(size = 14),
    # Increase the size of the facet strip text
    strip.text.x = element_text(size = 12),
    # Adjust text angle for State labels if necessary
    axis.text.y = element_text(angle = 0)
  )

@@

demobar$State <- factor(demobar$State, levels = c("Rajasthan", "Maharashtra","West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
demobar$age <- factor(demobar$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
demobar$urban_rural <- factor(demobar$urban_rural, levels = c("Rural","Urban"))
demobar$gender <- factor(demobar$gender, levels = c("Male","Female"))
demobar$caste <- factor(demobar$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
demobar$religion <- factor(demobar$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

@@

n_acceptreject<- module2 %>%
                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

@@

sum(is.na(formice))

@@

kahanfit4 <- psych::fa(mikahan$cov_combined, nfactors = 3, rotate = "varimax")

print.psych(kahanfit4, sort= TRUE, cut= 0.4)

@@

@@

fa_table(fit , .4) %>%
  rename(Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
  flex("Table 1: EFA on adapted Cultural Cognition Scale from Kahan et al(2007)", col_widths = list(Items = 4.5, Code = 1))

@@

```{r, echo = FALSE}
fit[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Egalitarianism = MR1, Communitarianism = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Table 2: Eigenvalues and Variance Explained for Cultural Cognition Scale")
```

@@

nkahanall <- kahanallscores %>%
  rowwise() %>%
  mutate(
    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2"))),
    K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

@@

## Kahan corelation table
```{r}

cor(nkahanall)

#before mice 
 cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))

#after mice
 cor.plot(nkahanall)

cov(nkahanall)

## Kahan scater plot from EFA scores 
```{r, echo = FALSE}

nkahanfinal %>%
  ggplot(aes(MR1, MR2))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=0, colour="black", lwd=0.5)+
  geom_vline(xintercept=0, colour="black", lwd=0.5)+
  labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
  ylim(-2,3)+
  xlim(-2,3)+
  theme_minimal() 
```

# Kahan alpha test

KahanallHE <-nkahanall %>%
  dplyr::select(starts_with(c("K_H", "K_E")))

KahanallHE_alpha <- psych::alpha(KahanallHE, check.keys = TRUE) # alpha = 0.71

KahanallC <-nkahanall %>%
  dplyr::select(starts_with(c("K_S")))

KahanallC_alpha <- psych::alpha(KahanallC, check.keys = TRUE) # alpha = 0.73

@@

# PRIDENUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "PRIDENUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the PRIDENUCLEAR variable.")

@@

miecopol <- mifa(data= ecopoln,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

@@

ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 50, seed = 429, print = FALSE), "broad")

@@

# Eco-pol alpha test

nPdevelop <-necopol %>%
  dplyr::select((c(BEAUTYNUCLEAR,  HEALTHNUCLEAR,  POLLUTENUCLEAR, DISPLACENUCLEAR, OWNERPUB, ENVOVERDEV)))

nPdevelop_alpha <- psych::alpha(nPdevelop, check.keys = TRUE) # alpha = 0.79

nNdevelop <-necopol %>%
  dplyr::select((c(DEVNUCLEAR, PROSPERNUCLEAR,PRIDENUCLEAR, NPRIDENUCLEAR, JOBSNUCLEAR, ECONOMYGLOBAL,          WEALTHLIM,INDUSTRYLARGE, DECISIONCEN, MECHANISATION )))

nNdevelop_alpha <- psych::alpha(nNdevelop , check.keys = TRUE) # alpha = 0.79

@@

radar4 <- rbind(max_min2, wide_loadings_df2) %>%
    rename(
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Limits on Wealth " = "WEALTHLIM",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Pro Centralisation" = "DECISIONCEN",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Anti Regulations" = "OWNERNOREG",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Less Reliance on government(nuclear)" = "RELYNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Environment over Development" = "ENVOVERDEV",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Localeconomy" = "ECONOMYLOCAL",
    )

@@

```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='70', out.height='70'}
library(fmsb)

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.7), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 2,
    # Customize the axis
    axislabcol = "black", cexc = 7, # Increase label size for axis
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
    seg = 7, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 4,
    ...
  )
}

@@

# Pretty table: Nuclear EFA

@@

rename_map2 <- c(
  "WEALTHLIM" = "A limit should be put to how much wealth a person can amass",
  "MECHANISATION" = "Rapid mechanization of work is taking away jobs from workers in this country",
  "DECISIONDECEN" = "Local politicians shouldn't have to ask permission from the central government to implement policies",
  "DECISIONCEN" = "Laws and policies would be implemented more smoothly if more power lay with the central government",
  "INDUSTRYLARGE" = "Large scale industries are required for the development of the country that will benefit everyone",
  "INDUSTRYSMALL" = "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  "ECONOMYGLOBAL" = "Foreign companies have led to a range of benefits for the Indian people and society",
  "ECONOMYLOCAL" = "India would be better off if foreign companies didn't come to here",
  "ENVOVERDEV" = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  "DEVOVERENV" = "Economic growth and creating jobs should be prioritized over environmental protection",
  "OWNERPVT" = "All businesses and industries should be owned privately",
  "OWNERNOREG" = "There is too much red-tape and the government should not interfere with businesses and industries",
  "OWNERPUB" = "The government should own most large businesses and industries",
  "OWNERREG" = "Regardless of ownership, the government should pass strong regulations and implement them",
  "DISPLACENUCLEAR" = "Nuclear energy is leading to displacement of people from their land",
  "BEAUTYNUCLEAR" = "Nuclear energy spoils the natural beauty of the landscape",
  "POLLUTENUCLEAR" = "Nuclear energy increases pollution of air/water/land",
  "HEALTHNUCLEAR" = "Nuclear energy poses a great risk to the health of people living around it",
  "JOBSNUCLEAR" = "Nuclear energy will bring jobs to the local community",
  "PRIDENUCLEAR" = "I would be proud if my community used nuclear energy",
  "NPRIDENUCLEAR" = "Nuclear energy is a mark of pride for our nation",
  "DEVNUCLEAR" = "Nuclear energy pushes forward the country's development",
  "PROSPERNUCLEAR" = "Nuclear energy brings economic prosperity to the surrounding regions",
  "RELYNUCLEAR" = "I don't like the idea that I have to rely on the government for electricity from nuclear energy"
)

@@

fa_table(ecopolfit2, .4) %>%
  rename(Ndevelop = MR1, Pdevelop = MR2, Items= item) %>%
  dplyr::mutate(code = case_when(
    code == "WEALTHLIM" ~ "Limits on Wealth",
    code == "MECHANISATION" ~ "Anti Mechanisation of work",
    code == "DECISIONDECEN" ~ "Pro Decentralisation",
    code == "DECISIONCEN" ~ "Pro Centralisation",
    code == "INDUSTRYLARGE" ~ "Pro Large Industries",
    code == "INDUSTRYSMALL" ~ "Anti Large Industries",
    code == "ECONOMYGLOBAL" ~ "Pro Globaleconomy",
    code == "ECONOMYLOCAL" ~ "Pro Localeconomy",
    code == "ENVOVERDEV" ~ "Environment over Development",
    code == "DEVOVERENV" ~ "Development over Environment",
    code == "OWNERPVT" ~ "Pro Private ownership",
    code == "OWNERNOREG" ~ "Anti Regulations",
    code == "OWNERPUB" ~ "Pro Public ownership",
    code == "OWNERREG" ~ "Pro Regulations",
    code == "DISPLACENUCLEAR" ~ "Displacement risk(nuclear)",
    code == "POLLUTENUCLEAR" ~ "Pollution risk(nuclear)",
    code == "HEALTHNUCLEAR" ~ "Health risk(nuclear)",
    code == "JOBSNUCLEAR" ~ "Job opportunities(nuclear)",
    code == "BEAUTYNUCLEAR" ~ "Spoils Natural Beauty(nuclear)",
    code == "PROSPERNUCLEAR" ~ "Local prosperity(nuclear)",
    code == "PRIDENUCLEAR" ~ "Community pride(nuclear)",
    code == "NPRIDENUCLEAR" ~ "National pride(nuclear)",
    code == "DEVNUCLEAR" ~ "National development(nuclear)",
    code == "RELYNUCLEAR" ~ "Less Reliance on government(nuclear)",
    TRUE ~ code # Default case to keep original value if no match
  )) %>%
  flex("Table 3: EFA on Eco-Pol Values Scale", col_widths = list(Items = 4.5, code = 1.5))

@@

```{r, echo = FALSE}
ecopolfit2[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Ndevelop = MR1, Pdevelop = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Table 4: Eigenvalues and Variance Explained Eco-Pol Scale")
```

@@

kahannuclear <- fct_scores%>%
  rename(Egalitarian = MR1, Communitarian = MR2)

@@

# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
#pred[, "Uppercaste"] <- 0
#pred[, "Male"] <- 0
#pred[, "Hindu"] <- 0
#pred[, "Age"] <- 0
#pred[, "Ndevelop"] <- 0
#pred[, "Pdevelop"] <- 0
#pred[, "Egalitarian"] <- 0
#pred[, "Communitarian"] <- 0
# Identify columns that start with "K_" and set them to 0
#k_columns <- grep("^K_", colnames(formice1))
#pred[, k_columns] <- 0

@@

nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice)

nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice)

@@

kahannuclear2 <- fct_scoresk2%>%
  rename(Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice2)

nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice2)

@@

kahannuclear3 <- fct_scoresk3%>%
  rename(Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice3)

nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice3)

@@

kahannuclear4 <- fct_scoresk4%>%
  rename(Egalitarian = MR1, Communitarian = MR2)

@@

nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformice4)

nuclearIVmiceimp34 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformice4)

@@

kahannuclearfinal <- nkahanfinal%>%
  rename(Egalitarian = MR1, Communitarian = MR2)

@@

allformicefinal$State <- factor(allformicefinal$State, levels = c("Maharashtra","West Bengal" ,"Rajasthan","Tamil Nadu",  "Uttar Pradesh"))

@@

nuclearfinal3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian, data = allformicefinal)

nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal)

summary(nuclearfinal)
summary(nuclearfinal2)
summary(nuclearfinal3)
summary(nuclearfinal4)

aic_values <- AIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)

print(aic_values)

bic_values <- BIC(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4)

print(bic_values)

# correlation table

```{r}

nforcor <- allformicefinal %>%
           dplyr::select(Risky_Nuclear, Communitarian , Egalitarian , Pdevelop , Ndevelop)

cor.plot(nforcor)
```

# interaction vars

```{r}

nuclearinterac <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian*State + Egalitarian*State + Pdevelop*State + Ndevelop*State , data = allformicefinal)

summary(nuclearinterac)

```
\newpage

@@
